\documentclass{40k}

\input{mission-list}
\fourbysix

\begin{document}

\pagetitle{The Tournament of Blood}

\begin{columns}

\missionheading{Army Construction}

Armies must be selected to at most~\underline{1850 points}.

No model with more than~9 hull points or wounds is permitted.
Superheavy vehicles and gargantuan creatures are otherwise allowed.

No other requirements or constraints are placed on detachments,
formations, or force organization. An optional Quick Reaction Force
detachment is made available for this event, described below.

\missionheading{Sources}

Forge World units and armies eligible for standard \emph{Warhammer
  40,000}, i.e., not \emph{Apocalypse}, are permitted. Units and
armies from Forge World's Horus Heresy \emph{Age of Darkness} books
are also permitted.

All up-to-date, official \emph{Warhammer 40,000} and \emph{Age of
  Darkness} army sources are permitted that are available in current
publication. This does include White Dwarf entries, which are
available via back issues, and current campaign books. It does not
include limited edition dataslates and formations, e.g., those
included in mega-bundles. Contact the event organizer(s) beforehand
about any questions. Remember that you must have all sources on hand.

For any codex or supplement (re-)released within two weeks preceding
the event, players may choose whether to use the old or new
edition. They may not use both editions of a single source within the
event, e.g., allying old with new.

\missionheading{Models}

Models need not be painted, but painting scores will be applied to
overall standings to reward finished armies, in addition to a seperate
painting and hobby competition.  Models must be WYSIWYG, but
identifiable and thoughtful conversions and proxies are
welcome. Indistinguishable or confusing proxies are not
permitted. Contact the organizer(s) with questions.

\missionheading{Materials}

Each player must bring typed, printed copies of your army lists for
event staff and their opponents.

You must have an official, legal, complete physical or digital copy on
hand for all army, unit, and other sources you are using. You should
bring printed copies of relevant pages of any electronic
sources. Don't forget errata and FAQs for your sources, available from
Games Workshop's Rules Errata webpage.

You must bring any dice, templates, and markers needed to facilitate
playing your army.

\missionheading{Quick Reaction Force}

Players may optionally employ a Quick Reaction Force detachment in
their lists, defined as follows.

\missionsubheading{Force Organization.}

An army may only contain a single Quick Reaction Force detachment.
All units in the detachment must have the same faction, or have no
faction.  The detachment is comprised of units from the following
battlefield roles.

\definecolor{ltgray}{gray}{0.8}

\bigskip\centerline{\begin{tabular}{ccc}
\rowcolor{ltgray} {\bf HQ} & {\bf Troop} & {\bf Elite}\\
1--2 & 2--6 & 1--4
\end{tabular}}

\smallskip\centerline{\begin{tabular}{ccc}
\rowcolor{ltgray} {\bf Fast Attack} & {\bf Heavy Support} & {\bf Lord of War}\\
$\star$ & $\star$ & 0--1
\end{tabular}}

A Quick Reaction Force detachment must include one Fast Attack and one
Heavy Support choice. It may include up to three selections in one of
those roles, but must contain one and only one selection in the other
role. I.e., the detachment must adhere to one of the following
options, excluding dedicated transports as usual:

\begin{itemize}\shortlist
\item 1--3 Fast Attack and 1 Heavy Support
\item 1 Fast Attack and 1--3 Heavy Support
\end{itemize}

\missionsubheading{Command Benefits}

The following advantages are granted for utilizing this detachment:

\begin{itemize}\shortlist
\item \textbf{Objective Secured.} All scoring units in this detachment
  except superheavy vehicles, gargantuan creatures, and fortifications
  gain Objective Secured. A unit with this special rule controls
  objectives even if an enemy scoring unit is within range of the
  objective marker, unless the enemy unit also has this rule.

\item \textbf{QRF Commander.} f this detachment is your primary
  detachment, instead of rolling a random warlord trait you may choose
  a warlord trait from the tables in the main \emph{Warhammer 40,000}
  rulebook. If you wish to use a different table of warlord traits,
  i.e., from a codex, then you must roll a random trait, but may
  reroll the result.
\end{itemize}

\missionheading{Schedule}

The tournament has~3 rounds, each game~2.5 hours long.  There will be
a break for dinner on your own.

\missionheading{Scoring}

Overall tournament rankings and the winner of The Tournament of Blood
are based on points earned toward a maximum of~100 available for the
day:
\begin{itemize}\shortlist
\item 60 points for match results
\item 25 points for painting and craftsmanship
\item 15 points for sportsmanship
\end{itemize}

Prizes will also be awarded for painting and craftsmanship based on
player voting, separate from the painting and craftsmanship scoring.
The latter reflects a minimum standard of preparedness while the
voting and prizes award masterful work.

Pure competition standings, i.e., the Best General prize(s) if
awarded, are determined first by win/draw/loss records and then the
sum total victory points earned across all three missions.



%Scoring is divided into three components: Match results, painting \&
%craftsmanship, and sportsmanship.

\missionsubheading{Match Results}

Match results are determined by scoring primary, secondary, and
tertiary objectives as given for each mission.  The winner is the
player with more victory points at game end.  Players draw if they
have earned equal victory points.  No more than~20 victory points may
be earned per mission.  Primary objectives award at most~9,
secondaries at most~6, and tertiaries at most~5 victory points.

Match results are a simple sum of the victory points earned in each
mission, up to 20 points each.

\missionsubheading{Painting and Craftsmanship}

Painting and craftsmanship is scored objectively by the organizer(s)
applying the following rubric to the armies.

\medskip%
\centerline{\begin{tabular}{|L{2.5in}c|}
\multicolumn{2}{c}{\emph{\bf Appearance Standard}}\\
\hline
  All models assembled and primed & +5 pts\\
\rowcolor{ltgray} All models three-color minimum & +5 pts\\
  All models based (paint/flock) & +5 pts\\
\rowcolor{ltgray} Advanced painting techniques present (washes, drybrushing, etc) & +5 pts\\
  Advanced basing techniques present (grass, sculpting, etc.) & +5 pts\\
\hline
\end{tabular}}

% \begin{itemize}\shortlist
% \item All models assembled and primed: +5 pts
% \item All models three-color minimum: +5 pts
% \item All models based (paint/flock): +5 pts
% \item Advanced painting techniques present (washes, drybrushing, etc): +5 pts
% \item Advanced basing techniques present: +5 pts
% \end{itemize}

\missionsubheading{Sportsmanship}

Each round players submit a sportsmanship score for their opponent.
By default players receive~5 sportsmanship points each round, from
which points are docked by the following rubric.

\medskip%
\centerline{\begin{tabular}{|L{2.5in}c|}
\multicolumn{2}{c}{\emph{\bf Negative Behavior}}\\
\hline
Openly hostile or rude & -3 pts\\
\rowcolor{ltgray}Unnecessarily competitive in army list or attitude & -2 pts\\
Sloppy with measuring, moving, line of sight, or dice & -2 pts\\
\rowcolor{ltgray}Unreasonably late, overly slow play, or too inattentive & -1 pts \\
Significantly unfamiliar with rules or made too many mistakes & -1 pts\\
\rowcolor{ltgray}Not prepared with clear, readable, typed army lists & -1 pts\\
\hline
\end{tabular}}


\missionheading{Warmaster}

Independent of overall standings, each player will also be scored on
Warlord Achievements accomplished in each game.  The player who
secures the greatest number of warlord achievements across all games
will be declared Warmaster and earn a prize.

\medskip%
\centerline{\begin{tabular}{|L{3in}|}
\multicolumn{1}{c}{\emph{\bf Warlord Achievements}}\\
\hline
Your warlord survived the game.\\
\rowcolor{ltgray} All enemy warlords were removed as casualties, by any means.\\
Your warlord challenged an enemy warlord at least once.\\
\rowcolor{ltgray} Your warlord or an attached unit eliminated an enemy warlord.\\
Your warlord eliminated an opponent in at least one challenge.\\
\rowcolor{ltgray} Your warlord or an attached unit won at least one close combat.\\
Your warlord or an attached unit eliminated at least one enemy unit through shooting.\\
\rowcolor{ltgray} Your warlord or an attached unit scored an objective marker at least once this game.\\
Your warlord is wholly within the enemy deployment zone.\\
\rowcolor{ltgray} Your warlord is at least partially within 6'' of the table center point.\\
\hline
\end{tabular}}

\missionheading{Pairings}

First round match pairs are randomized.  Second and third rounds
follow Dutch Swiss pairing: Players are grouped by win/draw/loss and
ranked within each group by total victory points.  In groups with an
odd number, the lowest ranked player shifts into the next best group.
Within each group, the highest ranked player is paired to the lowest
ranked player, the 2nd highest player to the 2nd lowest player, and so
on.

\end{columns}

\input{common-rules}

\input{mission1}
\input{mission2}
\input{mission3}
\end{document}
