%%----------------------------------------------------------------------
%%----------------------------------------------------------------------
\missiontitle{Mission 3: Graveyard}

\begin{tablesetup}

  \vanguardstrike

  \smallskip%
  Roll off and in that order alternate placing one primary objective
  marker in each other's deployment zones, neutral territory, and then
  your own deployment zones.

\end{tablesetup}

%%----------------------------------------------
\begin{missionrules}

\bigskip
There are no rules specific to this mission.

\end{missionrules}

%%----------------------------------------------
\begin{scoring}  
\begin{primaries}

  In deployment order but before any deployment begins, each player in
  turn generates their primary objectives as follows.  Roll a D6 on
  the following list to nominate four primary objectives for yourself,
  rerolling any duplicates.  Your opponent chooses one of the four,
  and then you choose two others.  The three chosen are your primary
  objectives.  \underline{Remember you may earn at most 9 victory
    points from primaries.}

  \begin{enumerate}\shortlist
  \item Each primary objective marker in your opponent's deployment
    zone is worth 3 points.

  \item Control the primary objective marker at table center at game
    end for~3 victory points.

  \item Choose and declare one of the primary objective markers in
    your opponent's table corners and earn~3 victory points if you
    control it at game end.

  \item Earn~1 victory point at game end for each primary objective
    marker controlled, up to a total of~3 victory points; a marker
    cannot be scored for both this objective and objectives~A or~B.

  \item Earn~3 victory points if at least 25\% of the opposing army by
    units is broken.

  \item Earn~3 victory points if at least 50\% of the opposing army by
    units is broken.

  \item Earn~1 victory point per quartile if at least 25\%, 50\%, and
    75\% of your army is \emph{not} broken.
  \end{enumerate}

  Units are considered broken if at game end they have been
  eliminated, are falling back, are in reserve, or have at most~25\%
  of their starting models remaining.
\end{primaries}

\begin{secondaries}
\interrogation
\seekanddestroy
\reconnaissance
\breachpoints
\end{secondaries}

\end{scoring}
