%%----------------------------------------------------------------------
%%----------------------------------------------------------------------
\missiontitle{Mission 3: Battlefield}

\begin{tablesetup}

  \dawnofwar

  \smallskip%
  Place a primary objective marker 16'' x 16'' from each table corner,
  and a fifth at table center.

\end{tablesetup}

%%----------------------------------------------
\begin{missionrules}

  \bigskip%
  There are no rules specific to this mission, just those applied to
  all in this packet.

\end{missionrules}

%%----------------------------------------------
\begin{scoring}  
\begin{primaries}
  Simultaneously with declaring secondary objectives, both players
  choose and declare three of the following primary scoring mechanisms
  for themselves, \underline{earning at most 9 victory points}:

  \begin{enumerate}[label=\Alph*.]\shortlist
  \item Control the primary objective marker at table center at game
    end for~3 victory points.

  \item Choose and declare one of the primary objective markers in
    your opponent's table corners and earn~3 victory points if you
    control it at game end.

  \item Earn~1 victory point at game end for each primary objective
    marker controlled, up to a total of~3 victory points; a marker
    cannot be scored for both this objective and objectives~A or~B.

  \item Earn~3 victory points if at least 25\% of the opposing army by
    units is broken.

  \item Earn~3 victory points if at least 50\% of the opposing army by
    units is broken.

  \item Earn~1 victory point per quartile if at least 25\%, 50\%, and
    75\% of your army is \emph{not} broken.
  \end{enumerate}

  Units are considered broken if at game end they have been
  eliminated, are falling back, are in reserve, or have at most~25\%
  of their starting models remaining.
\end{primaries}

\begin{secondaries}
\assassination
\meatgrinder
\reconnaissance
\breachpoints
\end{secondaries}

\end{scoring}
