%%----------------------------------------------------------------------
%%----------------------------------------------------------------------
\missiontitle{Mission 1: Aggression}

%\teaser{Recon forces desperately searching for weaknesses in the enemy
%  lines collide!}

%%----------------------------------------------
\begin{tablesetup}

  \dawnofwar

  \bigskip%
  After selecting deployment zones, roll off on D6.  In that order,
  both players alternate placing one primary objective marker each in
  their opponent's deployment zone, and then one in the neutral ground
  outside both zones, for a total of~4 markers on the table.

\end{tablesetup}

%%----------------------------------------------
\begin{missionrules}

  \missionsubheading{Take Command.} Units joined by an independent
  character HQ model gain the Obective Secured rule, as defined on
  rulebook page~122.

\end{missionrules}


%%----------------------------------------------
\begin{scoring}
  
\begin{primaries}

  Before any Scout redeployments, both players secretly choose one of
  the following primary scoring mechanisms for themselves:

  \begin{itemize}
  \item {\textit{Continuous.}} Beginning with Turn~2, score~1 victory
    point at the end of each of your player turns for each primary
    objective marker you control.

  \item {\textit{End Game.}} At game end, score~3 victory points for
    each primary objective marker you control.

  \end{itemize}
  This selection is declared along with the choice of secondary
  objective, below.  Remember that \underline{no more than}
  \underline{9 victory points may be earned toward primary
    objectives}.

\end{primaries}

\begin{secondaries}
  \overrun

  \assassination

  \meatgrinder

  \seizeground
\end{secondaries}

\end{scoring}
