%%----------------------------------------------------------------------
%%----------------------------------------------------------------------
\clearpage
\missiontitle{Common Rules}

The following rules are to be applied in each mission of this packet.

\begin{columns}
  
\missionheading{Startup Sequence}
Each mission will use the following setup process:

\begin{itemize}\shortlist
\item Clarify terrain and exchange lists

\item Determine warlord traits, then psychic powers, and then other
  pre-game effects and choices

\item D6 roll off to select deployment zones

\item Place primary objective markers

\item D6 roll off to choose first or second deployment

\item Deploy main armies in that order

\item Deploy any Infiltrators (pg. 167)

\item Secretly choose and record secondary objectives from the options
  listed for the mission

\item Make any Scout redeployments (pg. 171)

\item Reveal secondary objectives

\item First to deploy chooses to play first or second

\item Seize the Initiative roll, if desired

%\item \emph{Fight!}
\end{itemize}

\missionheading{Mission Rules}

Standard objective placement constraints apply unless noted otherwise
by a specific mission.

The following special rules are applied to each mission unless
specifically noted otherwise, in addition to any given by the mission
definition or otherwise specified, e.g., for a particular table.

\missionsubheading{Easy Recon.}  Players add~+1 to their roll to
choose first or second deployment for each superheavy vehicle or
gargantuan creature in the opposing army.

\missionsubheading{Reserves.} As defined on page~135 of the main
\emph{Warhammer 40,000} rulebook.

\missionsubheading{Seize the Initiative.} As defined on page~132 of
the main \emph{Warhammer 40,000} rulebook.

\missionsubheading{Variable Game Length.} As defined on page~133 of
the main \emph{Warhammer 40,000} rulebook.

\missionsubheading{All In.}  Units/models in reserve at game end count
as completely destroyed/removed as a casualty.

\end{columns}

\missionheading{Tertiary Objectives}

Both players apply all of the following tertiary objectives in each
mission.  \underline{No more than~5 total victory points}
\underline{may be earned by a player across all of the tertiary
  objectives.}

\begin{itemize}
\item \textit{Victory Through Attrition.}  Score~1 victory point for
  every~2 unsaved hull points or wounds suffered by an opposing
  superheavy vehicle or gargantuan creature through any means,
  including explosions and other indirect effects.  These points are
  earned at the end of any phase in which such damage occurs, and thus
  include any repaired or regenerated later.

\item \textit{Slay the Warlord.}  If the opposing army has a Lord of
  War character or a Warlord of any type and either has been removed
  as a casualty or is falling back at the end of the game, score~2
  victory points.

\item \textit{Linebreaker.}  Score~2 victory points if a model from
  any friendly scoring unit is completely within 12'' of your
  opponent's table edge.

\item \textit{First Blood.}  As defined on page~133 of the main
  \emph{Warhammer 40,000} rulebook.

\item \textit{Special Conditions.}  Any unit, faction, formation, or
  other special rules granting victory points to either player are
  considered tertiary objectives and are included within the~5 point
  cap.
\end{itemize}
