%%----------------------------------------------------------------------
%%----------------------------------------------------------------------
\clearpage
\missiontitle{Mission 1: Grind}

\centerline{\emph{}}

\missionheading{Table Setup}

\hammerandanvil


\bigskip%
After determining deployment zones, place five primary objective
markers: One at the center of the table worth~3 victory points; two
more 18'' from the short table edges and 24'' from the long table
edges worth~2 points each; and two~36'' from the short table edges and
12'' from the long table edges worth~1 point each.

\missionheading{Mission Specific Rules}

The following mission specific rules apply, in addition to those
applied to all missions in this pack.

\missionsubheading{Strike Force.}  All Fast Attack units have the
Obective Secured rule, as defined on page~122 of the rulebook.

%\missionsubheading{Nightfighting.}  All units have Stealth on Turn 1.



\missionheading{Scoring}

This mission is scored by objectives achieved, as follows.

\missionsubheading{Primary Objectives.}  Each primary objective marker
is worth their respective value given above.


\missionsubheading{Secondary Objectives.}

After deployment, both players simultaneously choose and then reveal a
single secondary objective for themselves from the list below.  Any
necessary selections are chosen and then revealed with the objective
unless noted otherwise.  \underline{No more than~6 victory points may
  be earned via any secondary.}

\begin{itemize}
\item \textit{Seize Ground.}  Choose two terrain pieces not in your
  deployment zone.  Do not declare these now, but do secretly record
  your selection unambiguously!  Reveal these at game end and score~3
  victory points for each piece that you control, treating them as
  objective markers.  Note that this means a single unit cannot claim
  both a primary objective marker and a terrain piece simultaneously.

\item \textit{Seek and Destroy.}  Choose and declare a Battlefield
  Role other than Troop.  Score~2 victory points for each enemy unit
  of this role completely destroyed or falling back at the end of the
  game.

\item \textit{Assassinate.}  Score~1 victory point for each opposing
  character model removed as a casualty or falling back at the end of
  the game.  Note that this is not limited to just independent
  characters.
\end{itemize}

\tertiaries
