%%----------------------------------------------------------------------
%%----------------------------------------------------------------------
\clearpage
\missiontitle{Mission 3: Into the Maelstrom}

\centerline{\emph{Now deep into the conflict, plans and strategies
    begin to fall apart.}}

\missionheading{Table Setup}

Deployment zones are \textbf{Vanguard Strike}, as defined on page~131
of the main \emph{Warhammer 40,000} rulebook.  Vanguard Strike may be
approximated by deploying within a 33.5'' x 50'' table corner
triangle.  The player that wins the zone roll off may pick any of the
four corners, and the other player takes that diagonally opposite.

\bigskip%
After determining deployment zones, roll off on~D6 and in that order
alternate placing objective markers.  Each player must place their
first marker in their opponent's deployment zone, their second in
neither zone, and their third in their own deployment zone.  Label
these markers~1 through~6, in any fashion.

\bigskip%
Both players receive their own table of tactical objectives, attached.


\missionheading{Mission Specific Rules}

At the start of each of your turns, do the following until you have 3
tactical objectives in play: Roll a~D66 and consult your tactical
objective table.  If that objective is already in play for you, has
been achieved, or is scratched off, roll again.  Similarly, if that
objective would be provably impossible to score, e.g., your opponent
has no characters remaining, roll again.  Once a valid objective has
been rolled, mark it as in play.

Targets cannot be nominated or chosen for a tactical objective marked
with a $\dagger$ that have already been chosen for a $\dagger$
objective you have in play.

\smallskip
At the end of your turns, check the requirements for each tactical
objective you have in play.  For each fixed-value objective met, mark
it as achieved and score the associated value in \emph{tactical
  points} (n.b.: not \emph{victory points}).  Tactical objectives with
a value of X may be kept in play as long as you wish.  At the end of
your any of your turns while in play they may be marked as achieved
and scored as indicated.  Once achieved, objectives are no longer
considered in play and cannot be put in play or scored again.

Multiple objectives can be scored in a turn, caveat that you cannot
achieve multiple tactical objectives with the same exact title in the
same turn using the same marker(s) or unit(s).  E.g., to score both
Storm objectives at once, you would need to simultaneously control two
separate markers in the enemy deployment zone.

At the end of your turn you may scratch out one of your tactical
objectives in play to remove it from play.

\smallskip
Tactical objectives in play, achieved, and scratched out are not secret.


\missionheading{Scoring}

This mission is scored by objectives achieved, as follows.

\missionsubheading{Primary Objectives.}

At game end, compare tactical points earned through tactical
objectives achieved and award victory points to the higher and lower
scorer as follows:

%\definecolor{Gray}{gray}{0.9}
%\definecolor{DGray}{gray}{0.75}
\newcolumntype{a}{>{\columncolor{gray!25}}c}
\newcolumntype{b}{>{\columncolor{gray!50}}r}
\bigskip\centerline{\setlength{\tabcolsep}{12pt}%
\begin{tabular}{|b|c|a|c|a|c|a|}
\hline
{\bf Difference}     & 0     & 1--2  & 3--4  & 5--6  & 7     & 8+\\
{\bf Victory Points} & 4 / 4 & 5 / 4 & 6 / 3 & 7 / 2 & 8 / 1 & 9 / 0\\
\hline
\end{tabular}}

% \begin{squishitemize}
%\item Difference of 0 Mission points = 4 - 4
%\item Difference of 1-2 MP = 5 - 4
%\item Difference of 3-4 MP = 6 - 3
%\item Difference of 5-6 MP = 7 - 2
%\item Difference of 7 MP = 8 - 1
%\item Difference of 8+ MP = 9 - 0
%\end{squishitemize}

\missionsubheading{Secondary Objectives.}

After deployment, both players simultaneously choose and then reveal a
single secondary objective for themselves from the list below.  Any
necessary selections are chosen and then revealed with the objective
unless noted otherwise.  \underline{No more than~6 victory points may
  be earned via any secondary.}

\begin{itemize}
\item \textit{Break Their Back.}  At game end, each enemy unit that
  has been eliminated, is falling back, or has at most~25\% of its
  starting models remaining is broken.  Earn~2 victory points per
  quartile if at least 25\%, 50\%, and 75\% of your opponent's army by
  units is broken.

\item \textit{Hold the Field.}  At game end, earn~2 victory points
  for every~2 primary objectives held.

\end{itemize}

\tertiaries

\clearpage

\newcounter{tonum}
\newcounter{tomajor}

\newcommand\toblocktitle{\setcounter{tomajor}{1}\toblocktitledraw}
\WithSuffix\newcommand\toblocktitle*{\toblocktitledraw}

\newcommand{\toblocktitledraw}{%
%\pagetitle{Primary Objectives}
\renewcommand{\arraystretch}{1.2}%
\noindent\hfill\begin{tabular}{F{2em}F{1em}F{1em}F{1em}F{1in}m{4.7in}}%4.7in
%\rowcolor{gray!50}
{\bf \#} & \hbox to 10pt{\hspace{-2pt}\rotatebox{45}{\bf In Play}}  & \hbox to 10pt{\hspace{-2pt}\rotatebox{45}{\bf Achieved}} & \hbox to 10pt{\hspace{-2pt}\rotatebox{45}{\bf Value}} & {\bf Title} & {\bf Requirement} \\
\end{tabular}\hfill\hbox to 0pt{}
}

\newenvironment{toblock}
{%
\setcounter{tonum}{1}
\rowcolors{1}{gray!25}{white}%
\renewcommand{\arraystretch}{1.3}%
\noindent\hfill\begin{tabular}{|C{2em}C{1em}C{1em}C{1em}C{1in}m{4.7in}|}
\hline
%\rowcolor{gray!50}
%{\bf \#} & \hbox to 10pt{\hspace{-2pt}\rotatebox{45}{\bf Drawn}}  & \hbox to 10pt{\hspace{-2pt}\rotatebox{45}{\bf Earned}} & \hbox to 10pt{\hspace{-2pt}\rotatebox{45}{\bf Points}} & {\bf Title} & {\bf Requirement} \\
%\hline
}
{%
\hline
\end{tabular}\hfill\hbox to 0pt{}
\stepcounter{tomajor}
}

\newcommand{\toset}{\setcounter{tonum}{1}\stepcounter{tomajor}}

\newcommand{\cardline}[3]{%
\thetomajor-\thetonum\stepcounter{tonum} & $\Box$ & $\Box$ & #3 & {\bf #1} & #2\\
}
% \raisebox{12pt}{\checkbox} & \raisebox{12pt}{\checkbox} 

\newcommand\tocard[3]{\cardline{#1}{#2}{#3}}
\WithSuffix\newcommand\tocard*[3]{\cardline{#1}{#2}{#3} [12pt]}

\newcommand{\totitle}[1]{%
\noindent\begin{tikzpicture}
\node [blackbox] (box){%
\vbox to 10pt {\vfil\hbox to \ttlwidth {\hfil%
\hbox {\color{white}\Large\bf\sc\fontfamily{ptm}\selectfont #1}
\hfil}\vfil%
}};%
\end{tikzpicture}%
%\vspace*{14pt}
}

\clearpage
\squelchbackground
\begin{landscape}

\vspace*{-15pt}
\centerline{\scalebox{1.25}{\Large\bf\sc\fontfamily{ptm}\selectfont Tactical Objectives}}

\vspace{-24pt}
%\hrule
\vbox to 0pt{}

\noindent
\begin{minipage}[t][\textheight-0.25in][t]{0.5\linewidth-1em}
\resizebox{\linewidth}{!}{%
\begin{minipage}[t]{7.5in}%
\vbox to 0pt{}
\input{tactical-objectives-1}%
\end{minipage}}

\vfill
\small

Tactical objectives with a value of X may be kept in play as long as
you wish.  At the end of your any of your turns while in play they may
be marked as achieved and scored as indicated.

\smallskip%
Targets cannot be nominated or chosen for a tactical objective marked
with a $\dagger$ that have already been chosen for a $\dagger$
objective you have in play.

\smallskip%
Multiple tactical objectives with the exact same title cannot be
achieved at the same time using the same markers or opposing units.
\end{minipage}
\hfill
\begin{minipage}[t][\textheight-0.25in][t]{0.5\linewidth-1em}
\resizebox{\linewidth}{!}{%
\begin{minipage}[t]{7.5in}%
\vbox to 0pt{}
\input{tactical-objectives-2}%
\end{minipage}}

\vfill
\small

Immediately reroll any objectives provably impossible to achieve.

\smallskip%
No aspect of these tactical objectives is to be kept secret.
\end{minipage}

%\vfill
%\hrule
\end{landscape}

\clearpage
\restorebackground
