%%----------------------------------------------------------------------
%%----------------------------------------------------------------------
\clearpage
\missiontitle{Mission 2: Forced March}

\centerline{\emph{The armies begin the long maneuvers from their drop
    sites to the targets of their campaign.}}

\missionheading{Table Setup}

Deployment zones are \textbf{Hammer and Anvil}, as defined on page~131
of the main rulebook (24'' short edges).

\bigskip%
In each of the four table corners place a primary objective marker
12'' from both of the table edges of that corner.  Place a fifth
primary objective marker at the center of the table.

\missionheading{Mission Specific Rules}

The following mission specific rules apply, in addition to those
applied to all missions in this pack.

\missionsubheading{The Longest Day.}  After Turn~4 roll a D6; on a~4+
all units have Stealth for the remainder of the game.  Do this again
after Turn~5 if it did not take effect.  This rule automatically takes
effect after Turn~6.


\missionheading{Scoring}

This mission is scored by objectives achieved, as follows.

\missionsubheading{Primary Objectives.} At the conclusion of the game,
players score~1 victory point for each objective they control in their
own deployment zone and~2 points for the marker at table center.
Players earn~3 additional victory points if they control one marker in
the enemy deployment zone, and~5 points if they control both.

\missionsubheading{Secondary Objectives.}

After deployment, both players simultaneously choose and then reveal a
single secondary objective for themselves from the list below.  Any
necessary selections are chosen and then revealed with the objective
unless noted otherwise.  \underline{No more than~6 victory points may
  be earned via any secondary.}

\begin{itemize}
\item \textit{Control the Field.}  Each table quarter in which you
  have a scoring unit and your opponent does not, or you have an
  Objective Secured Unit and your opponent does not, is worth 2
  victory points.

\item \textit{Seek and Destroy.}  Choose and declare a Battlefield
  Role other than Troop.  Score~2 victory points for each enemy unit
  of this role completely destroyed or falling back at the end of the
  game.

\item \textit{Meatgrinder.}  Score~1 victory point for each opposing
  Troop unit destroyed or falling back at game end.

\end{itemize}

\tertiaries
