%%----------------------------------------------------------------------
%% Deployment Zones
%%----------------------------------------------------------------------

\newcommand{\dawnofwar}%
{Deployment zones are \textbf{Dawn of War}, as on page~131 of the
\emph{Warhammer 40,000} rulebook (12'' long edges).}

\newcommand{\hammerandanvil}%
{Deployment zones are \textbf{Hammer and Anvil}, as defined on
  page~131 of the main rulebook (24'' short edges).}

\newcommand{\vanguardstrike}%
{Deployment zones are \textbf{Vanguard Strike}, as defined on page~131
  of the main \emph{Warhammer 40,000} rulebook.  Vanguard Strike may
  be approximated by deploying within a 33.5'' x 50'' table corner
  triangle.  The player that wins the zone roll off may pick any of
  the four corners, and the other player takes that diagonally
  opposite.}

\newcommand{\quartered}%
{Deployment zones are the rectangles in each table corner~12'' in from
  the long edge and~24'' in from the short edges.  The player that
  wins the zone roll off picks either pair of \emph{diagonally
    opposite} corners as their deployment zone and a long table edge
  as their player edge.  The other player takes the other pair of
  diagonally opposite corners and opposite long edge.}

%%----------------------------------------------------------------------
%% Secondaries
%%----------------------------------------------------------------------


%%----------------------------------------------------------------------
%% Secondaries
%%----------------------------------------------------------------------

\newcommand{\seekanddestroy}%
{\item \textit{Seek and Destroy.}  Choose and declare a Battlefield
  Role other than Troop.  Score~2 victory points for each enemy unit
  of this role completely destroyed or falling back at the end of the
  game.}

\newcommand{\seizeground}%
{\item \textit{Seize Ground.}  Choose two terrain pieces not in your
  deployment zone.  Do not declare these now, but do secretly record
  your selection unambiguously!  Reveal these at game end and score~3
  victory points for each piece that you control, treating them as
  objective markers.  Note that this means a single unit cannot claim
  both a primary objective marker and a terrain piece simultaneously.}

\newcommand{\reconnaissance}%
{\item \textit{Reconnaissance.}  At the end of the game, score~2
  victory points for each friendly scoring unit with the Scout or
  Infiltrate USR completely within 12'' of your opponent's table
  edge.}

\newcommand{\meatgrinder}%
{\item \textit{Meatgrinder.}  Score~1 victory point for each opposing
  Troop unit completely destroyed or falling back at the end of the
  game.}

\newcommand{\assassination}%
{\item \textit{Assassination.}  Score~1 victory point for each
  opposing character model removed as a casualty or falling back at
  the end of the game.  Note that this is not limited to just
  independent characters.}

\newcommand{\controlthefield}%
{\item \textit{Control the Field.}  Each table quarter in which you
  have a scoring unit and your opponent does not, or you have an
  Objective Secured Unit and your opponent does not, is worth 2
  victory points.}


%%----------------------------------------------------------------------
%% Tertiaries
%%----------------------------------------------------------------------

\newcommand{\tertiaries}%
{\missionsubheading{Tertiary Objectives.}
  As given in the overall Common Rules section of this packet.}
