\toblocktitle

\begin{toblock}
\tocard{Hold~1}{Control marker~\#1.}{1}
\tocard{Hold~2}{Control marker~\#2.}{1}
\tocard{Hold~3}{Control marker~\#3.}{1}
\tocard{Hold~4}{Control marker~\#4.}{1}
\tocard{Hold~5}{Control marker~\#5.}{1}
\tocard{Hold~6}{Control marker~\#6.}{1}
\end{toblock}

\bigskip
\begin{toblock}
\tocard{Advance}{Control a marker outside both deployment zones.}{1}%
\tocard{Advance}{Control a marker outside both deployment zones.}{1}%
 \tocard{Storm}{Control a marker in your
  opponent's deployment zone.}{2}%
\tocard{Storm}{Control a marker in your opponent's deployment
  zone.}{2}%
\tocard{Defend}{Control all markers in your deployment zone; cannot
  claim Turn 1.}{2}%
\tocard{Defend}{Control all markers in your deployment zone; cannot
  claim Turn 1.}{2}%
\end{toblock}

\bigskip
\begin{toblock}
  \tocard{Hill King}{You have a non-flying scoring unit
    wholly within~6'' of table center and your opponent does not.}{1}%
%
\tocard{Frontline Leader}{Your warlord is wholly within the opponent's
  deployment zone.}{1}%
%
\tocard{Field Commander}{Your warlord is within 3'' of a marker you
  control, outside your zone.}{1}%
%
\tocard{Butcher}{While this objective is in play, mark one of these
  boxes each time an opposing non-vehicle unit is removed from play:
  \hfill $\Box$ $\Box$ $\Box$ $\Box$\newline At the end of any of your
  turns while you have this objective in play, you may remove it from
  play without counting that against your discard.  When you do so,
  earn 1 tactical point for each marked box.}{X}%
%
\tocard{Assassin}{While this objective is in play, mark one of these
  boxes each time an opposing character is removed from play: \hfill
  $\Box$ $\Box$ $\Box$ $\Box$\newline At the end of any of your turns
  while you have this objective in play, you may remove it from play
  without counting that against your discard.  When you do so, earn 1
  tactical point for each marked box.}{X}%
%
\tocard{Dominator}{Your opponent controls no markers and you control
  at least 2.}{4}%

\end{toblock}
