\documentclass[nobackground]{40k}

\newcommand{\checkbox}{\raisebox{-1pt}{\fbox{\hbox to 1em{\vbox to 1em{}}}}}

\newcommand{\letterbox}{\fbox{\hbox to 2em{\vbox to 32pt{}}}}

\newcommand{\scorebox}{\fbox{\hbox to 64pt{\vbox to 64pt{}}}}

\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}


\newcommand{\ballots}{%
\noindent
\rotatebox{90}{\begin{minipage}{3.25in}\centering
\begin{story}{58pt}{Painting Display}\large
\textbf{This is:}

\vbox to 40pt{}

\hrule

\bigskip
\textbf{By:}

\vbox to 40pt{}
\hrule

\smallskip\centerline{\scriptsize (place with your army during player
  voting!)}
\end{story}
\end{minipage}}
%%
\hfill
%%
\rotatebox{90}{\begin{minipage}{3.25in}\centering
\begin{story}{60pt}{Painting Votes}\large

  Vote for your favorite armies by painting and craftsmanship:

\bigskip
1.

\vspace{4pt}
\hrule

\bigskip
2.

\vspace{4pt}
\hrule

\bigskip
3.

\vspace{4pt}
\hrule
\end{story}
\end{minipage}}
%%
\hfill
%%
\rotatebox{90}{\begin{minipage}{3.25in}\centering
\begin{story}{84pt}{Sportsmanship Ranking}\large
  Rank your opponents 1/2/3 by which you enjoyed most:

Mission 1:
\hfill
\letterbox

\vspace{4pt}
\hrule

\bigskip
Mission 2:
\hfill
\letterbox

\vspace{4pt}
\hrule

\bigskip
Mission 3:
\hfill
\letterbox

\vspace{4pt}
\hrule
\end{story}
\end{minipage}}
}

\begin{document}

\ballots

\vfill

\ballots

\vfill

\ballots

\end{document}

%\bigskip\noindent
Both players please complete a scoresheet at the conclusion of each
match and turn in to the judge(s).

\smallskip \centerline{\large\textbf{\textit{Double check your scoring
      conditions and points earned, and write legibly!!!}}}

% \bigskip
% \centerline{
%\begin{minipage}[c]{1.35in}\flushright\bf
%Mission \#
%\end{minipage}~
%\begin{minipage}[c]{6in}
%\letterbox   
%\end{minipage}
%}

\vfill
\bigskip\noindent{\Huge\bf Mission \#\;\raisebox{-7pt}{\fbox{\hbox to 1em{\vbox to 32pt{}}}}}

\bigskip
\centerline{
\begin{minipage}[c]{1.35in}\flushright\bf
Your Name
\end{minipage}~
\begin{minipage}[c]{6in}
\letterbox\ \ 
\letterbox\ \ 
\letterbox\ \ 
\letterbox\ \ 
\letterbox\ \ 
\letterbox\ \ 
\letterbox\ \ 
\letterbox\ \ 
\letterbox\ \ 
\letterbox\ \ 
\letterbox\ \ 
\letterbox\ \ 
\letterbox\ \ 
\letterbox   
\end{minipage}
}

\bigskip
\centerline{
\noindent\begin{minipage}[c]{1.35in}\flushright\bf
Opponent's Name
\end{minipage}~
\begin{minipage}[c]{6in}
\letterbox\ \ 
\letterbox\ \ 
\letterbox\ \ 
\letterbox\ \ 
\letterbox\ \ 
\letterbox\ \ 
\letterbox\ \ 
\letterbox\ \ 
\letterbox\ \ 
\letterbox\ \ 
\letterbox\ \ 
\letterbox\ \ 
\letterbox\ \ 
\letterbox   
\end{minipage}
}

\vfill
\bigskip\noindent{\Huge\bf Victory Points}

\smallskip\noindent%
Record victory points earned, not the number of objectives claimed.
Include as tertiary objectives any victory points earned through
special objectives offered by your opponent's rules and mark here if
this occurred: \checkbox

\bigskip\centerline{
\begin{tabular}{R{0.75in} C{1in} c C{1in} c C{1in} c C{1in}}
&
\textbf{\textit{Primary Objectives}} & &
\textbf{\textit{Secondary Objective}} & &
\textbf{\textit{Tertiary Objectives}} & &
\textbf{\textit{Total}}
\\
\textbf{You} &
\scorebox & \bf + &
\scorebox & \bf + &
\scorebox & \bf = &
\scorebox\\
\textbf{Opponent} &
\scorebox & \bf + &
\scorebox & \bf + &
\scorebox & \bf = &
\scorebox
\end{tabular}
}

\bigskip\noindent%
Which secondary objective did you play for?~~~~~~
\checkbox~\#1~~~~
\checkbox~\#2~~~~
\checkbox~\#3~~~~
\checkbox~\#4

%\bigskip\noindent\textbf{Sportsmanship}

%\vspace*{-4pt}

\vfill
\bigskip\noindent{\Huge\bf Sportsmanship}

\smallskip\noindent%
Check the appropriate box below for your experience in this match.  At
the end of the day, each player will additionally be asked to rank
their opponents by which they enjoyed playing the most.

\smallskip\noindent\hfill
\begin{minipage}{2in}\bf
  How much did you enjoy playing your opponent?
\end{minipage}
\hfill
\begin{minipage}{4.75in}
\smallskip\noindent\raisebox{-2pt}{\checkbox}~ (3) Best game ever---I'd invite them to my house for the rematch!

\smallskip\noindent\raisebox{-2pt}{\checkbox}~ (2) Pretty average game of 40K.

\smallskip\noindent\raisebox{-2pt}{\checkbox}~ (1) Below average game of 40K.

\smallskip\noindent\raisebox{-2pt}{\checkbox}~ (0) I would forfeit before playing them again.
\end{minipage}
\hfill
\hbox to 0pt{}

\smallskip\noindent%
If you checked box \#0, ``I would forfeit,'' please talk to the
judge(s) about what went wrong with your match.

\vfill
\bigskip\noindent{\Huge\bf Painting}

\smallskip\noindent%
Armies are objectively scored for painting and craftsmanship by the
judge(s).  The simple requirement metrics for this are in the scoring
guide.  Make sure your army gets evaluated before the end of the day!

In addition, each player will be given a ballot before the dinner
break to vote for their favorite army, unit, or model, whatever
strikes their fancy.  Make sure to have your army out on display at
that point to compete, and to highlight features and marquee models to
your opponents and spectators throughout the day.

\end{document}
