%%----------------------------------------------------------------------
%%----------------------------------------------------------------------
\missiontitle{Mission 1: Forge Your Alliance}

\teaser{}

%%----------------------------------------------
\begin{tablesetup}

  Deployment zones are each the two table corners sharing a long table
  edge, up to 12'' from the long table edge and 24'' from the short
  edges.  The team that wins the roll off to pick deployment zone
  chooses a long table edge and takes both corners along that edge.
  Both teams then secretly record which of their players will deploy
  into which of the two corners in their deployment zone.

  \bigskip%
  After each team has secretly recorded its players' corners, place a
  single primary objective marker at table center.  The teams then
  roll off on D6 and alternate in that order placing a single primary
  objective marker in each of their deployment zone corners, for a
  total of 5 objectives on the table.

  \bigskip%
  On each team's turn to deploy it reveals which player will deploy
  into which corner, and then they do so simultaneously.  All of the
  models deployed in each of the team's table corners must be from the
  detachment(s) of the player declared for that corner.

  Infiltrating models are not restricted by the table corner
  declarations.

\end{tablesetup}

%%----------------------------------------------
\begin{missionrules}

\nightfighting
\end{missionrules}


%%----------------------------------------------
\begin{scoring}
  
\begin{primaries}

  At game end the primary objective marker at table center is worth 3
  victory points.  For each team the markers in the opposing team's
  deployment zone are worth 2 victory points each, and the markers in
  its own deployment zone 1 victory point each.

\end{primaries}

\begin{secondaries}
  \seizeground

  \seekanddestroy

  \meatgrinder
\end{secondaries}

\end{scoring}
