%%----------------------------------------------------------------------
%% Decorations
%%----------------------------------------------------------------------

\newcommand{\teaser}[1]{\centerline{\emph{#1}}}

%%----------------------------------------------------------------------
%% Deployment Zones
%%----------------------------------------------------------------------

\newenvironment{tablesetup}
{\missionheading{Table Setup}}
{}

\newcommand{\dawnofwar}%
{Deployment zones are \textbf{Dawn of War}, as on page~131 of the
\emph{Warhammer 40,000} rulebook (12'' long edges).}

\newcommand{\hammerandanvil}%
{Deployment zones are \textbf{Hammer and Anvil}, as defined on
  page~131 of the main rulebook (24'' short edges).}

\newcommand{\vanguardstrike}%
{Deployment zones are \textbf{Vanguard Strike}, as defined on page~131
  of the main \emph{Warhammer 40,000} rulebook.  Vanguard Strike may
  be approximated by deploying within a 33.5'' x 50'' table corner
  triangle.  The team that wins the zone roll off may pick any of
  the four corners, and the other team takes that diagonally
  opposite.}

\newcommand{\quartered}%
{Deployment zones are the rectangles in each table corner~12'' in from
  the long edge and~24'' in from the short edges.  The team that
  wins the zone roll off picks either pair of \emph{diagonally
    opposite} corners as their deployment zone and a long table edge
  as their team edge.  The other team takes the other pair of
  diagonally opposite corners and opposite long edge.}

%%----------------------------------------------------------------------
%% Mission Rules
%%----------------------------------------------------------------------

\newenvironment{missionrules}
{
\missionheading{Mission Specific Rules}

The following mission specific rules apply, in addition to those
applied to all missions in this packet.
}
{
}

\newcommand{\nightfighting}%
{\missionsubheading{Night Fighting.}  As defined on page~135 of the
main rulebook: If either team opts for Night Fighting before any
deployment begins, on a single D6 of 4+ all units have Stealth
throughout Turn 1.}


%%----------------------------------------------------------------------
%% Scoring
%%----------------------------------------------------------------------

\newenvironment{scoring}{
\missionheading{Scoring}

This mission is scored by objectives achieved, as follows.
}
{
\tertiaries
}

\newenvironment{primaries}
{
\missionsubheading{Primary Objectives.}  
}
{}


%%----------------------------------------------------------------------
%% Secondaries
%%----------------------------------------------------------------------

\newenvironment{secondaries}
{
\missionsubheading{Secondary Objectives.}

After deployment, both teams simultaneously choose and then reveal a
single secondary objective for themselves from the list below.  Any
necessary selections are chosen and then revealed with the objective
unless noted otherwise.  \underline{No more than~6 victory points may
  be earned via any secondary.}

\begin{itemize}
}
{
\end{itemize}
}

\newcommand{\seekanddestroy}%
{\item \textit{Seek and Destroy.}  Choose and declare a Battlefield
  Role other than Troop.  Score~2 victory points for each enemy unit
  of this role completely destroyed or falling back at the end of the
  game.}

\newcommand{\breachpoints}%
{\item \textit{Breach Points.}  Choose two terrain pieces at least
  partially in the opposing deployment zone.  Do not declare these
  now, but do secretly record your selection unambiguously!  Reveal
  these at game end and score~3 victory points for each piece that you
  control, treating them as objective markers.  Note that this means a
  single unit cannot claim both a primary objective marker and a
  terrain piece simultaneously.}

\newcommand{\seizeground}%
{\item \textit{Seize Ground.}  Choose two terrain pieces not in your
  deployment zone.  Do not declare these now, but do secretly record
  your selection unambiguously!  Reveal these at game end and score~3
  victory points for each piece that you control, treating them as
  objective markers.  Note that this means a single unit cannot claim
  both a primary objective marker and a terrain piece simultaneously.}

\newcommand{\reconnaissance}%
{\item \textit{Reconnaissance.}  At the end of the game, score~2
  victory points for each friendly scoring unit with the Scout or
  Infiltrate USR completely within 12'' of your opponent's table
  edge.}

\newcommand{\meatgrinder}%
{\item \textit{Meatgrinder.}  Score~1 victory point for each opposing
  Troop unit completely destroyed or falling back at the end of the
  game.}

\newcommand{\assassination}%
{\item \textit{Assassination.}  Score~1 victory point for each
  opposing character model removed as a casualty or falling back at
  the end of the game.  Note that this is not limited to just
  independent characters.}

\newcommand{\controlthefield}%
{\item \textit{Control the Field.}  Each table quarter in which you
  have a scoring unit and your opponent does not, or you have an
  Objective Secured Unit and your opponent does not, is worth 2
  victory points.}

\newcommand{\breaktheirback}%
{\item \textit{Break Their Back.}  At game end, each enemy unit that
  has been eliminated, is falling back, or has at most~25\% of its
  starting models remaining is broken.  Earn~2 victory points per
  quartile if at least 25\%, 50\%, and 75\% of your opponent's army by
  units is broken.}

\newcommand{\stalwart}%
{\item \textit{Stalwart.} Score~2 victory points for each primary
  objective marker held at game end.}

\newcommand{\holdthefield}%
{\item \textit{Hold The Field.} Score~2 victory points for every~2
  objective markers held at game end.}

%%----------------------------------------------------------------------
%% Tertiaries
%%----------------------------------------------------------------------

\newcommand{\tertiaries}%
{\missionsubheading{Tertiary Objectives.}
  As given in the overall Common Rules section of this packet.}
